Meta-analysis of the Interoceptive Accuracy Scale

### 2025-08-27 analysis/figures/table2.tex
manuscript updated
collapsed 1) phq2/GAD into PHQ4 ; 2) STAI5-T into STAIT  + Updated sample table
table 2 updated
need to add references

\begin{table}
\fontsize{6.8pt}{8.1pt}\selectfont
\begin{tabular*}{\linewidth}{@{\extracolsep{\fill}}lrlrr}
\toprule
Questionnaire & Number of Dimensions & Assessment & Number of Items & Scoring \\ 
\midrule\addlinespace[2.5pt]
{\bfseries Interoceptive Related} &  &  &  &  \\ 
MAIA-2 & 8 & Interoception & 37 & 6-point Likert scale \\ 
BPQ & 2 & Body awareness and autonomic reactivity & 49 & 5-point Likert scale \\ 
TAS-20 & 3 & Alexithymia & 20 & 5-point Likert scale \\ 
BVAQ & 2 & Alexithymia & 40 & 5-point Likert scale \\ 
{\bfseries Mood} &  &  &  &  \\ 
BDI-II & 1 & Severity of depressive symptoms & 21 & 0-to-3-point values \\ 
PHQ-4 & 2 & Anxiety and depressive symptoms & 4 & 5-point Likert scale \\ 
STAI-T & 1 & Trait anxiety & 20 & 4-point Likert scale \\ 
GAD-2 & 1 & General Anxiety & 2 & 4-point Likert scale \\ 
{\bfseries Personality} &  &  &  &  \\ 
NEO-FFI & 1 & Neuroticism & 12 & 5-point Likert scale \\ 
Mini IPIP6 & 6 & Personality & 24 & Analogue scales \\ 
BFI & 5 & Personality & 44 & 5-point Likert scale \\ 
PID-5-SF & 5 & Dysfunctional personality traits & 25 & 4-point Likert scale \\ 
{\bfseries Psychopathology} &  &  &  &  \\ 
SPQ-BRU & 4 & Schizotypy & 32 & 5-point Likert scale \\ 
MSI-BPD & 1 & Borderline personality disorder & 10 & Analogue scales \\ 
ASQ - Short & 5 & Autistic Traits & 28 & 4-point Likert scale \\ 
{\bfseries Beliefs and Misbeliefs} &  &  &  &  \\ 
GCB & 5 & Conspiracy beliefs & 15 & 5-point Likert scale \\ 
PI-18 & 1 & Beliefs about the world & 99 & 6-point Likert scale \\ 
LIE scale & 4 & Lying tendencies & 16 & Visual analogue scales \\ 
\bottomrule
\end{tabular*}
\end{table}

>>>>

\begin{table}[t]
\fontsize{6.8pt}{8.1pt}\selectfont
\begin{tabular*}{\linewidth}{@{\extracolsep{\fill}}lrlrrl}
\toprule
Questionnaire & Number of Dimensions & Assessment & Number of Items & Scoring & Example\_Items \\ 
\midrule\addlinespace[2.5pt]
{\bfseries Interoceptive Related} &  &  &  &  &  \\ 
MAIA-2 & 8 & Interoceptive awareness & 37 & 6-point Likert scale & I notice when I am uncomfortable in my body \\ 
BPQ-SF & 2 & Body awareness and autonomic reactivity & 46 & 5-point Likert scale & My heart often beats irregularily \\ 
BPQ-VSF & 1 & Body awareness & 12 & 5-point Likert scale & My mouth being dry \\ 
ICQ & 3 & Interoceptive confusion & 20 & 5-point Likert scale &  I cannot tell when my muscles are sore or tight \\ 
TAS-20 & 3 & Alexithymia & 20 & 5-point Likert scale & I have feelings I can't quite identify \\ 
BVAQ & 5 & Alexithymia & 40 & 5-point Likert scale & I like to tell others how I feel \\ 
{\bfseries Mood} &  &  &  &  &  \\ 
BDI-II & 2 & Depressive symptoms severity & 21 & 4-point scale & I feel sad much of the time \\ 
PHQ-4 & 2 & Depression and Anxiety & 4 & 4-point Likert scale & Little interest or pleasure in doing things \\ 
PHQ-9 & 1 & Depressive symptoms & 9 & 4-point Likert scale & Feeling tired or having little energy? \\ 
PHQ-15 & 1 & Somatic symptom distress & 15 & 3-point scale & Over the last week, how often have you been bothered by back pain? \\ 
MFQ & 1 & Mood and affect & 13 & 3-point scale & I felt miserable or unhappy \\ 
STAI-T & 1 & Trait anxiety & 20 & 4-point Likert scale & I worry too much about something that really doesn't matter \\ 
GAD-7 & 1 & General anxiety disorder symptoms & 7 & 4-point Likert scale & Not being able to stop or control worrying \\ 
{\bfseries Personality} &  &  &  &  &  \\ 
NEO-FFI (neuroticism subscale) & 1 & Neuroticism & 12 & 5-point Likert scale & I often feel inferior to others \\ 
Mini IPIP6 & 6 & Personality traits & 24 & Visual analogue scales & Am the life of the party \\ 
BFI-S & 5 & Personality traits & 10 & 7-point Likert scale & I see myself as someone who ...is considerate and kind to almost everyone \\ 
{\bfseries Psychopathology} &  &  &  &  &  \\ 
PID-5-SFF & 5 & Maladaptive personality traits & 25 & 4-point Likert scale & Plenty of people are out to get me \\ 
SPQ-BR & 9 & Schizotypy & 32 & 5-point Likert scale & I am an odd, unusual person \\ 
MSI-BPD & 1 & Borderline personality disorder & 9 & Dichotomous (yes/no) & Have any of your closest relationships been troubled by a lot of arguments or repeated breakups? \\ 
ASQ - Short & 5 & Autistic traits & 28 & 4-point Likert scale & I find it difficult to work out people’s intentions \\ 
{\bfseries Beliefs and Misbeliefs} &  &  &  &  &  \\ 
GCBS & 5 & Conspiracy beliefs & 15 & 5-point Likert scale & Secret organizations communicate with extraterrestrials, but keep this fact from the public \\ 
PI-18 & 3 & Primal world beliefs & 18 & 5-point Likert scale & Nearly everything in the world is beautiful \\ 
LIE scale & 4 & Lying tendencies & 16 & Visual analogue scales & I am a good liar \\ 
\bottomrule
\end{tabular*}
\end{table}

### 2025-08-27 analysis/study2.qmd
table 2 updated
need to add references

@@

table <- data.frame(
  Questionnaire = c("Interoceptive Related", "MAIA-2", "BPQ", "TAS-20", "BVAQ",
                    "Mood", "BDI-II", "PHQ-4", "STAI-T", "GAD-2",
                    "Personality", "NEO-FFI", "Mini IPIP6", "BFI", "PID-5-SF",
                    "Psychopathology", "SPQ-BRU", "MSI-BPD", "ASQ - Short",
                    "Beliefs and Misbeliefs", "GCB", "PI-18", "LIE scale"),
  Number_of_Dimensions = c('', 8, 2, 3, 2, 
                           '', 1, 2, 1, 1, 
                           '', 1, 6, 5, 5, 
                           '', 4, 1, 5, 
                           '', 5, 1, 4),
  Assessment = c('', "Interoception", "Body awareness and autonomic reactivity", "Alexithymia", "Alexithymia",
                 '',"Severity of depressive symptoms", "Anxiety and depressive symptoms", "Trait anxiety", "General Anxiety",
                 '', "Neuroticism", "Personality", "Personality", "Dysfunctional personality traits",
                 '', "Schizotypy", "Borderline personality disorder", "Autistic Traits",
                 '', "Conspiracy beliefs", "Beliefs about the world", "Lying tendencies"),
  Number_of_Items = c('',37, 49, 20, 40, 
                      '',21, 4, 20, 2, 
                      '',12, 24, 44, 25, 
                      '',32, 10, 28, 
                      '',15, 99, 16),
  Scoring = c('',"6-point Likert scale", "5-point Likert scale", "5-point Likert scale", "5-point Likert scale", 
              '',"0-to-3-point values", "5-point Likert scale", "4-point Likert scale", "4-point Likert scale", 
              '',"5-point Likert scale", "Analogue scales", "5-point Likert scale", "4-point Likert scale", 
              '',"5-point Likert scale", "Analogue scales", "4-point Likert scale", 
              '',"5-point Likert scale", "6-point Likert scale", "Visual analogue scales"), 
  stringsAsFactors = FALSE
)

@@

# names(df1a)
# names(df1b)
# names(df2)  #TAS, MAIA, ICQ, BPQ, BVAQ
# names(df3)  # TAS, BPQ
# names(df4)  # BPQ, PBCS (private bodily consciousness?), MAIA, BAQ, BRS
# names(df5)  
# names(df6)  # PHQ2, GAD2, SSS8, IATS
# names(df7a)  # STAIT, MAIA, CES (not reported in the paper), FFMQ, NEOFFI
# names(df7b)  # BPQ, PHQ15, PHQ9, MAIA, STAIT, 
# names(df7c)  # CI01 (not reported in the paper), TAS, BPQ, MAIA, ASI, ICQ 
# names(df8a)  # EDI, BPQ
# names(df8b)  # PHQ9, PHQ15, TAS
# names(df9)  # ECR (Experience in Close Relationship Scale), TEAQ (touch experiences and attitudes questionnaire), STQ, TACSEN, UCLA, BFI, DBIA, BO, EQ
# names(df10)  # ASQ, BPD, GCBS, IPIP6, LIE, MAIA, PHQ4, PI, PID, SPQ
# names(df11)  # PHQ4, STAIT5, BDI, MAIA
# names(df12) # MAIA, PI, 
# names(df13) # 
# names(df14) # MAIA, TAS, MFQ(DEP), STAI(ANX)
# names(df15) 
```

>>>>

- Note, GAD2 and PHQ2 were collapsed into phq4
- PI-99 was collapsed into PI-18

@@

table <- data.frame(
  Questionnaire = c(
    # Interoception
    "Interoceptive Related", "MAIA-2", "BPQ-SF", "BPQ-VSF", "ICQ", "TAS-20", "BVAQ",
    # Mood/Anxiety
    "Mood", "BDI-II", "PHQ-4", "PHQ-9", "PHQ-15", "MFQ", "STAI-T", "GAD-7",
    # Personality
    "Personality", "NEO-FFI (neuroticism subscale)", "Mini IPIP6", "BFI-S",
    # Psychopathology
    "Psychopathology", "PID-5-SFF", "SPQ-BR", "MSI-BPD", "ASQ - Short",
    # Beliefs and Misbeliefs
    "Beliefs and Misbeliefs", "GCBS", "PI-18", "LIE scale"
  ),
  Number_of_Dimensions = c(
    "", 8, 2, 1, 3, 3, 5,
    "", 2, 2, 1, 1, 1, 1, 1,
    "", 1, 6, 5,
    "", 5, 9, 1, 5,
    "", 5, 3, 4
  ),
  Assessment = c(
    "", "Interoceptive awareness", "Body awareness and autonomic reactivity", "Body awareness", "Interoceptive confusion", "Alexithymia", "Alexithymia", 
    "", "Depressive symptoms severity", "Depression and Anxiety", "Depressive symptoms", "Somatic symptom distress", "Mood and affect", "Trait anxiety", "General anxiety disorder symptoms",
    "", "Neuroticism", "Personality traits", "Personality traits",
    "", "Maladaptive personality traits", "Schizotypy", "Borderline personality disorder", "Autistic traits",
    "", "Conspiracy beliefs", "Primal world beliefs", "Lying tendencies"
  ),
  Number_of_Items = c(
    "", 37, 46, 12, 20, 20, 40,
    "", 21, 4, 9, 15, 13, 20, 7,
    "", 12, 24, 10,
    "", 25, 32, 9, 28,
    "", 15, 18, 16
  ),
  Scoring = c(
    "", "6-point Likert scale", "5-point Likert scale", "5-point Likert scale", "5-point Likert scale", "5-point Likert scale", "5-point Likert scale",
    "", "4-point scale", "4-point Likert scale", "4-point Likert scale", "3-point scale", "3-point scale", "4-point Likert scale", "4-point Likert scale",
    "", "5-point Likert scale", "Visual analogue scales", "7-point Likert scale",
    "", "4-point Likert scale", "5-point Likert scale", "Dichotomous (yes/no)", "4-point Likert scale",
    "", "5-point Likert scale", "5-point Likert scale", "Visual analogue scales"
  ),
  Example_Items = c(
    # Interoception
    "", "I notice when I am uncomfortable in my body", "My heart often beats irregularily", "My mouth being dry", " I cannot tell when my muscles are sore or tight", "I have feelings I can't quite identify", "I like to tell others how I feel",
    #Mood
    "", "I feel sad much of the time","Little interest or pleasure in doing things", "Feeling tired or having little energy?", "Over the last week, how often have you been bothered by back pain?", "I felt miserable or unhappy", "I worry too much about something that really doesn't matter", "Not being able to stop or control worrying",
    # Personality
    "", "I often feel inferior to others", "Am the life of the party", "I see myself as someone who ...is considerate and kind to almost everyone", 
   # Psychopathology
    "", "Plenty of people are out to get me", "I am an odd, unusual person", "Have any of your closest relationships been troubled by a lot of arguments or repeated breakups?", "I find it difficult to work out people’s intentions",
   # Beliefs and Misbeliefs
    "", "Secret organizations communicate with extraterrestrials, but keep this fact from the public", "Nearly everything in the world is beautiful", "I am a good liar"
),
  stringsAsFactors = FALSE
)

@@

# names(df1a)
# names(df1b)
# names(df2)  #TAS(20 items), MAIA(37 items), ICQ (20 items), BPQ(46 items), BVAQ (40 items)
# names(df3)  # TAS (20), BPQ (46)
# names(df4)  # BPQ(26), PBCS (private bodily consciousness?), MAIA (37), BAQ (18), BRS (4)
# names(df5)  
# names(df6)  # PHQ2 (2 items), GAD2 (2 items), SSS8, IATS
# names(df7a)  # STAIT (20), MAIA(37), CES (not reported in the paper), FFMQ (39), NEOFFI (12)
# names(df7b)  # BPQ (12), PHQ15 (15), PHQ9 (9), MAIA (37), STAIT(20), 
# names(df7c)  # CI01 (not reported in the paper), TAS, BPQ, MAIA, ASI, ICQ  - no individual items
# names(df8a)  # EDI (10), BPQ (12)
# names(df8b)  # PHQ9 (9), PHQ15 (15), TAS (20)
# names(df9)  # ECR (Experience in Close Relationship Scale), TEAQ (touch experiences and attitudes questionnaire), STQ, TACSEN, UCLA, BFI (15), DBIA, BO, EQ
# names(df10)  # ASQ(28), BPD(9), GCBS (15), IPIP6 (24), LIE (16), MAIA(37), PHQ4 (4), PI (32), PID (25), SPQ (32)
# names(df11)  # PHQ4 (4), STAIT5 (5), BDI (21), MAIA (37)
# names(df12) # MAIA (37), PI (99), 
# names(df13) # PI (18), MAIA (37)
# names(df14) # MAIA(37), TAS  (20), MFQ(DEP, 13), STAI(ANX, 20)
# names(df15) 
# names(df16) # MAIA (37), GAD (7), PHQ9 (9)
```
